### 2021-05-21 sections/2-info-theory.tex
A comment and a few additions

We extend the work from~\cite{berger2020levenshtein} for search and compression using a flat clustering to our case of a hierarchical clustering.
We further generalize this for any dataset and distance function described below.
We also provide relevant algorithms for some parings of datasets and distance functions in Section~\ref{subsec:methods:compression}.

We take a \textbf{dataset} $X$ with $n$ instances embedded in a $\mathcal{D}$-dimensional Banach Space defined by a distance function $f: X \times X \mapsto \mathbb{R}$.
We assume that the dataset follows the Manifold Hypothesis~\cite{fefferman2016testing}, i.e. instances in the dataset lie on a $d$-dimensional manifold where $d \ll \mathcal{D}$.
We also make some uniformity assumptions for the dataset;
specifically that $|X|$ is finite and the minimum and maximum sampling densities in the dataset differ by some constant multiplicative factor.

The \textbf{distance function} must have must be such that $\forall x, y, z \in X$:
\begin{enumerate}[i.]
    \item $f$ is deterministic.
    \item $f(x, y) = 0 \Leftrightarrow x = y$ and $f(x, y) > 0 \Leftrightarrow x \neq y$.
    \item $f(x, y) = f(y, x)$, i.e. symmetry.
    \item $f(x, z) \leq f(x, y) + f(y, z)$, i.e. the triangle inequality.
\end{enumerate}

@@

>>>>

We extend the work from~\cite{berger2020levenshtein} for search and compression using a flat clustering to our case of a hierarchical clustering.
We further generalize this for any dataset and distance function described below.
We also provide relevant algorithms for some pairings of datasets and distance functions in Section~\ref{subsec:methods:compression}.

We take a \textbf{dataset} $X$ with $n$ instances embedded in a $\mathcal{D}$-dimensional Banach space defined by a distance function $f: X \times X \mapsto \mathbb{R}$.
We assume that the dataset follows the Manifold Hypothesis~\cite{fefferman2016testing}, i.e. instances in the dataset mostly lie on a $d$-dimensional manifold where $d \ll \mathcal{D}$.
We also make some uniformity assumptions for the dataset;
specifically that $|X|$ is finite and the minimum and maximum sampling densities in the dataset differ by some constant multiplicative factor.

The \textbf{distance function} must be a metric; that is it must have the properties that $\forall x, y, z \in X$:
\begin{enumerate}[i.]
    \item $f$ is deterministic.
    \item $f(x, y) = 0 \Leftrightarrow x = y$ and $f(x, y) > 0 \Leftrightarrow x \neq y$.
    \item $f(x, y) = f(y, x)$, i.e. symmetry.
    \item $f(x, z) \leq f(x, y) + f(y, z)$, i.e. the triangle inequality.
\end{enumerate}

@@

% Wait, can't we encode any cluster at depth d with at most d bits? For a binary tree, arbitrarily choose 0 for left and 1 for right, and a length-d traversal uniquely identifies a cluster at depth d. Not sure if this is a weaker upper bound, but we should mention it. For n flat clusters, lg n bits identifies a unique one; for n leaves, lg n bits identifies a leaf, but an internal cluster at depth d only needs lg d bits.
% Actually I see that you sort of get at this in the "back to shannon entropy" subsection, but maybe it could be explained intuitively as I did above?

### 2021-05-21 sections/5-results.tex
typos, reorganization, and more
A comment and a few additions

\subsection{Asymptotic Complexity}
\label{subsec:results:asymptotic-complexity}

Analyze:
\begin{itemize}
    \item Building the tree.
    \item $\rho$-nearest neighbors search.
    \item k-nearest neighbors search.
    \item compression:
    \begin{itemize}
        \item encode (novel contribution)
        \item serialize
        \item compress
        \item decompress
        \item deserialize
        \item decode (novel contribution)
    \end{itemize}
\end{itemize}

\subsection{Benchmarks}
\label{subsec:results:benchmarks}

@@

@@

For each pair $(X, f)$ and a small selection of depths, measure:
\begin{enumerate}[1.]
    \item linear search vs accelerated search:
    \begin{enumerate}[i.]
        \item runtime performance,
        \item speedup factor, and
        \item number of distance comparisons.
    \end{enumerate}
    \item Compression CAKES + zlib vs just zlib, also substitute other libraries for zlib:
    \begin{enumerate}[i.]
        \item just the encoding vs the full dataset,
        \item encoding + serialization, and
        \item encoding + serialization + zlib.
    \end{enumerate}
\end{enumerate}

>>>>

@@

Ark: a 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM and CentOS 7 Linux with kernel 3.10.0-1127.13.1.el7.x86\_64 \#1 SMP. Rust 1.52, Python 3.6.8

Macbook Air: 8-core (4 performance, 4 efficiency) Apple M1 processor with 16GB RAM, macOS 11.3. Rust 1.52, Python 3.9.4

@@

For each pair $(X, f)$ and a small selection of depths, measure:
\begin{enumerate}[1.]
    \item linear search vs accelerated search:
    \begin{enumerate}[i.]
        \item runtime performance,
        \item speedup factor, and
        \item number of distance comparisons.
    \end{enumerate}
    \item Compression CAKES + zlib vs just zlib, also substitute other libraries for zlib:
    \begin{enumerate}[i.]
        \item just the encoding vs the full dataset,
        \item encoding + serialization, and
        \item encoding + serialization + zlib.
    \end{enumerate}
    \item Measure time taken for accelerated-search in the compressed space and decompression of the hits with different combinations of serde and codec libraries.
\end{enumerate}
